Scaling up the hyperparameter grid for Naomi

### 2023-07-11 src/dev_scale-grid/scale-grid.Rmd
Custom coordinate system AGHQ done #58

plot_points <- function(gg) {
  plot +
    geom_point(
      data = mvQuad::getNodes(gg) %>%
        as.data.frame() %>%
        mutate(weights = mvQuad::getWeights(gg)),
      aes(x = V1, y = V2, size = weights),
      alpha = 0.8,
      col = multi.utils::cbpalette()[2],
      inherit.aes = FALSE
    ) +
    scale_size_continuous(range = c(1, 2)) +
    labs(x = "", y = "", size = "Weight") +
    theme_minimal()
}

plot_points(grid_5) + plot_points(pca_grid_5) + plot_annotation(tag_levels = "A")
```

Try to create a grid similar to A above but using the second principal component rather than the first:

@@

custom_grid_5 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 1)
custom_grid_5$level <- rep(NA, times = 2)
custom_grid_5$ndConstruction <- "custom"
custom_grid_5$nodes <- nodes_out
custom_grid_5$weights <- weights_out

plot_points(grid_5) / plot_points(pca_grid_5) / plot_points(custom_grid_5) + plot_annotation(tag_levels = "A")

ggsave("pca-demo.png", h = 7, w = 6.25)
```

@@

We also know that any vector can be written in terms of the eigendecomposition.
For example, the vector `c(1, 1)` can be written as:

```{r}
a <- c(1, 1) %*% E

a[1] * E[, 1] + a[2] * E[, 2]
```

>>>>

plot_points <- function(gg) {
  plot +
    geom_point(
      data = mvQuad::getNodes(gg) %>%
        as.data.frame() %>%
        mutate(weights = mvQuad::getWeights(gg)),
      aes(x = V1, y = V2, size = weights),
      alpha = 0.8,
      col = multi.utils::cbpalette()[2],
      inherit.aes = FALSE
    ) +
    scale_size_continuous(range = c(1, 2)) +
    labs(x = "", y = "", size = "Weight") +
    theme_minimal()
}
```

Create a grid similar to A above but using the second principal component rather than the first:

@@

pc2_grid_5 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 1)
pc2_grid_5$level <- rep(NA, times = 2)
pc2_grid_5$ndConstruction <- "custom"
pc2_grid_5$nodes <- nodes_out
pc2_grid_5$weights <- weights_out
```

@@

We also know that any vector can be written in terms of the eigendecomposition:

```{r}
a <- c(1, 1) %*% E
a[1] * E[, 1] + a[2] * E[, 2]
```

We also have the definition of an eigenvalue and vector:

```{r}
sum(t(lambda[1] %*% E[, 1]) - C %*% E[, 1]) < 10e-12
```

The definition of the unit eigenvectors is that they maximise the amount of variation explained, which is given by this function `variance_explained`.
By definition `E[, 1]` maximises this!

```{r}
variance_explained <- function(v) {
  v %*% C %*% v / v %*% v
}

variance_explained(c(1, 1))
variance_explained(E[, 1])
```

```{r}
v <- c(1, 1)
v_norm <- v / sqrt(c(v %*% v))

gg_s <- mvQuad::createNIGrid(dim = 1, type = "GHe", level = 5)
nodes_out <- t(v_norm %*% sqrt(variance_explained(v_norm)) %*% t(mvQuad::getNodes(gg_s)))
for(j in 1:2) nodes_out[, j] <- nodes_out[, j] + m[j] # Adaption
weights_out <- mvQuad::getWeights(gg_s) * as.numeric(mvQuad::getWeights(mvQuad::createNIGrid(dim = 1, type = "GHe", level = 1)))
weights_out <- det(chol(C)) * weights_out # Adaption

v_norm_grid_5 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 1)
v_norm_grid_5$level <- rep(NA, times = 2)
v_norm_grid_5$ndConstruction <- "custom"
v_norm_grid_5$nodes <- nodes_out
v_norm_grid_5$weights <- weights_out

{plot_points(grid_5) + plot_points(pca_grid_5)} / {plot_points(pc2_grid_5) + plot_points(v_norm_grid_5)} + plot_annotation(tag_levels = "A")

ggsave("pca-demo.png", h = 6, w = 6.25)
```

## Application of custom coordinate system to scale standardised system

Now we apply what we've learnt about making grids with custom coordinate systems to make a grid with coordinate system defined by the eigendecomposition of the scale standardised variance matrix!

```{r}
#' TODO
```
